% 关键词，中文。用全角分号「；」分割
% 研究生的应首先从《汉语主题词表》中摘选
\ckeywords{Java；短视频应用；数据库优化；视频编码}

% 提交日期，本科生不需要
\cproddate{\the\year 年\the\month 月}

% 论文类型，中文，本科生不需要
% 从理论研究、应用基础、应用研究、研究报告、软件开发、设计报告、案例分析、调研报告、其它中选择
\ctype{}

% 论文标题，英文
\etitle{Short Video Application Development Based on SpringBoot and Wechat Application}

% 作者姓名，英文
\eauthor{Ziniu Lin}

% 学科，英文，本科生不需要
\esubject{}

% 导师姓名，英文
\esupervisor{Yongmei Gan}

% 关键词，英文。用半角分号和一个半角空格「; 」分割
\ekeywords{Java; Short Video Application; Database Optimization; Video Coding}

% 学科门类，英文
% 从Philosophy（哲学）、Economics（经济学）、Law（法学）、Education（教育学）、Arts（文学）、
%   Science（理学）、Engineering Science（工学）、Medicine（医学）、Management Science（管理学）中选择
\ecate{Engineering Science}

% 提交日期，英文，本科生不需要
% 应当和 cproddate 保持一致
\eproddate{\monthname{\month}\ \the\year}

% 论文类型，英文，本科生不需要
% 从Theoretical Research（理论研究）、Application Fundamentals（应用基础）、Applied Research（应用研究）、
%   Research Report（研究报告）、Software Development（软件开发）、Design Report（设计报告）、
%   Case Study（案例分析）、Investigation Report（调研报告）、其它（Other）中选择
\etype{}

% 摘要，中文。段间空行
\cabstract{
	随着无线通讯技术以及智能手机技术的发展，短视频应用获得了巨大的用户基数。短视频应用中比较重要的问题是如何保存大量的用户数据以及如何适当的处理用户上传的大量视频等。如何保存大量用户的数据的问题需要通过合理选择数据库架构、数据库模式以及一定的数据库优化解决。如何适当处理用户上传视频的问题需要通过设置合理地上传方式、视频压制方式以及合理地储存架构来解决。本文通过探寻短视频应用系统开发过程中的各个问题，找出了一些解决方案，这对于解决实际的工程问题以及探寻短视频应用的商业模式有着实际的作用。
	
	本文实现了数据库优化领域的成熟成果，实现了对于数据库系统两方面的优化。第一方面优化为参数优化，在基准测试的衡量下对数据库做整体的优化。第二方面为具体查询优化，针对某一应用、某一查询单独优化数据库系统。这些优化措施在数据库运行时取得了理想的结果。
	
	本文也对视频编码器以及视频压制中的硬件加速效果进行了验证。短视频系统的瓶颈之一就是视频编码器编码速度的问题。通过选用适合短视频应用场景的视频编码器以及使用硬件加速技术可以使得视频压制的过程尽快进行。本文主要通过硬件加速对编码过程进行优化，并且这些优化措施达到了预期目的。

}

% 摘要，英文。段间空行
\eabstract{
    With the development of wireless communication and smart phone, some short video application gains a lot of users. Some serious problems in the development of short video application are how can system store users' information properly and how can system handle the videos provided by users quickly and so on.The first question can be solved by choosing suitable database system structure and the optimization of the database. The second question can be solved by setting suitable upload method, proper video coding algorithm and using right storage method. This paper focus on these problems and get some solution of these problems. This paper will helpful to the solving of really problems and tracking the commercial mode of short video application.
    
    This paper implemented some mature achievements in database optimization and realized two aspects of database system optimization. The first aspect is attribute optimization, which is optimize the whole database under benchmarking. The second aspect is optimizing the database system independently for an application or query. These optimization work very well when the database was running.
    
    This paper also checked the codec and the hardware acceleration effect of video encoding and video compression. One of the bottlenecks of short video system is the encoding speed of video encoder. Through choosing proper video encoder and using hardware acceleration can make doing video compression quickly. This paper mainly optimizes the encoding process through hardware acceleration, and these optimization measures achieve the desired purpose.
}
